%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[8pt,a4paper]{article}

% Set the page margins.
\usepackage{geometry}
 \geometry{
 a4paper,
 tmargin=0.3in,
 lmargin=0.3in,
 rmargin = 0.5in,
 bmargin=0.5in
 }

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle {\Huge {\centerline{\textbf{ Kumar Shubham}}}}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\centerline{\noindent
\textsmaller{+}919790717731\sbull
\href{mailto:kumarshubham347@gmail.com}{Mail}\sbull
\href{https://github.com/krshubham}{Github} \sbull
\href{http://www.linkedin.com/in/krshubham1708}{Linkedin}\sbull
\href{https://krshubham.github.io}{Portfolio}}
\\
\large{\centerline{ \textit{{Move fast and break Things! If !(breaking) then !(fast)}}}}

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Education}

\headedsection
  {Vellore Institute of Technology}
  {\textsc{Chennai, India}} {%
  \headedsubsection
    {B.Tech, Computer Science}
    {2015 -- Present}
    {\begin{itemize}
        \item CGPA : 8.53/10 (After 2 semesters)
    \end{itemize}}
}


\spacedhrule{0em}{-0.4em}

\roottitle{Projects Developed}

\headedsection
  {\href{https://github.com/krshubham/codeslam}{Codeslam}}
  {\textsc{}}
  {\headedsubsection
        {Project Developer}
        {Oct 2016- Nov 2016}
        {
        \begin{itemize}
            \item {Web application for organizing programming workshops.}
            \item {Completely based on MEAN stack and RESTful practices.}
            \item {Built as a project for the Internet and Web Programming Cours.e}
        \end{itemize}
        }
    }
    
    \headedsection
  {\href{http://technovitchennai.com}{TechnoVIT Chennai}}
  {\textsc{}} {%
  \headedsubsection
    {Front end Lead}
    {Aug 2016- Sep 2016}
    {
        \begin{itemize}
            \item {Website for the annual Technical fest of VIT Chennai.}
            \item {Tech Stack: HTML,CSS,Google MDL, Responsive Web Design.}
            \item {Assisted team mates with version control systems like Git.}
            \item {Guide: Prof. Christy Jackson}
        \end{itemize}
        }
}

\headedsection
  {\href{http://krshubham.github.io/vibrance}{Vibrance VIT Chennai}}
  {\textsc{}} {%
  \headedsubsection
    {Technical and Front end lead}
    {Feb 2016- March 2016}
    {
        \begin{itemize}
            \item {Website for the annual Cultural fest of VIT Chennai}
 .           \item {Tech Stack: HTML,CSS,Javascript,Jquery}
 .           \item {Guide: Prof. Subbulakshmi T}
.        \end{itemize}
        }
}

\vspace{-0.2em}
\begin{center}
  \emph{}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{\textbf{Skills and Activities}}
\headedsection
  {\textbf{Technical:}}
  {\textsc{}} {%
  \headedsubsection
    {Web Application development}
    {}
    {\begin{itemize}
        \item {Front end: HTML5, CSS,JavaScript ES6,AngularJs, jQuery.}
        \item {Server side: Node with ExpressJs,MongoDB.}
        \item {DevOps: Parse,Selenium,AWS,Git.}
    \end{itemize}}
    \headedsubsection
    {Programming}
    {}
    {\begin{itemize}
        \item Familiar:Python(Flask), Java(JSP).
    \end{itemize}}
}

\headedsection
  {\textbf {Activities and awards:}}
  {\textsc{}} {%
  \headedsubsection
    {Open Source Contributions }
    {}
    {\begin{itemize}
        \item First prize on FOSS day for presenting a CNS system for drones with a team of 3.
    \end{itemize}}
    \headedsubsection
    {College Events}
    {}
    {\begin{itemize}
        \item First prize at Intra college Linux Quiz(2015).
        \item {Organizer and developer of the event and online platform respectively to spread coding culture in the college(2016).}
    \end{itemize}}
}

\headedsection
  {\textbf {Interests: }}
  {\textsc{}} {%
  \headedsubsection
    {Music to Academics:}
    {}
    {\begin{itemize}
        \item {\textbf{General interests:} Solving Problems, competitive coding,making automation scripts.}
        \item {\textbf{Course interests:} Programming,Compilers, Machine Learning, Artificial Intelligence,DBMS.}
        \item {\textbf{Free time:} EDM, Reading gadget reviews and watching dev conferences.}
        }
    \end{itemize}
    }
}

\end{document}

＀
